Concurrent Programming in Harmony

### 2022-01-10 book/paper.tex
Improved figure captions a bit

\begin{figure}
\begin{center}
\includegraphics[width=0.45\textwidth]{figures/hello3.png}
\end{center}
\begin{code}
<{:input:../code/hello3.hny}>
\end{code}
\caption{\harmonylink{code/hello3.hny} Two possible outputs}
\label{fig:choice}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=0.15\textwidth]{figures/hello4.png}
\end{center}
\begin{code}
<{:input:../code/hello4.hny}>
\end{code}
\caption{\harmonylink{code/hello4.hny} An infinite number of outputs}
\label{fig:hello4}
\end{figure}

\begin{figure}[h]
\begin{center}
\begin{tabular}{ccc}
\includegraphics[width=0.45\textwidth]{figures/hello5.png}
& \rule{0.05\linewidth}{0in} &
\includegraphics[width=0.45\textwidth]{figures/hello6.png} \\
\begin{tcolorbox}[width=0.4\linewidth]
<{:input:../code/hello5.hny}>
\end{tcolorbox}
& \rule{0.05\linewidth}{0in} &
\begin{tcolorbox}[width=0.4\linewidth]
<{:input:../code/hello6.hny}>
\end{tcolorbox}
\\
(a) \harmonylink{code/hello5.hny} && (b) \harmonylink{code/hello6.hny}
\end{tabular}
\end{center}
\caption{Methods and threads}
\label{fig:threads}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.9\textwidth]{figures/hello7.png}
\end{center}
\begin{code}
<{:input:../code/hello7.hny}>
\end{code}
\caption{\harmonylink{code/hello7.hny} Interleaving threads}
\label{fig:hello7}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=0.9\textwidth]{figures/hello8.png}
\end{center}
\begin{code}
<{:input:../code/hello8.hny}>
\end{code}
\caption{\harmonylink{code/hello8.hny} Less interleaving}
\label{fig:hello8}
\end{figure}

@@

\begin{figure}[h]
\begin{code}
<{:input:../code/Up.hny}>
\end{code}
\caption{\harmonylink{code/Up.hny} Incrementing twice in parallel}
\label{fig:inc}
\end{figure}

@@

\begin{figure}
\begin{code}
\VerbatimInput[xleftmargin=5mm,numbers=left]{../python/UpMany.py}
\end{code}
\caption{\harmonylink{python/UpMany.py} Incrementing <{N}> times}
\label{fig:incmany}
\end{figure}

@@

\begin{figure}
\begin{code}
<{:input:../code/UpEnter.hny}>
\end{code}
\caption{\harmonylink{code/UpEnter.hny} Broken attempt at fixing the code of \autoref{fig:inc}}
\label{fig:incenter}
\end{figure}

@@

\begin{figure}
\begin{code}
<{:input:../code/UpLock.hny}>
\end{code}
\caption{\harmonylink{code/UpLock.hny} Program of \autoref{fig:inc} fixed with a lock}
\label{fig:incfixed}
\end{figure}

@@

\begin{figure}
\begin{code}
<{:input:../code/locksusp.hny}>
\end{code}
\caption{\harmonylink{modules/synchS.hny} The lock implementation in the <{synchS}> module uses suspension}
\label{fig:suspension}
\end{figure}

@@

\begin{figure}
\begin{code}
<{:input:../code/xy.hny}>
\end{code}
\caption{\harmonylink{code/xy.hny} Incomplete code with desired invariant $x + y = 100$}
\label{fig:xy}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.9\textwidth]{figures/consensus.png}
\end{center}
\begin{code}
<{:input:../code/consensus.hny}>
\end{code}
\caption{\harmonylink{code/consensus.hny} Distributed consensus code and DFA}
\label{fig:consensus}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.95\textwidth]{figures/bosco.png}
\end{center}
\caption{The DFA for \autoref{fig:bosco}}
\label{fig:boscodfa}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=0.45\textwidth]{figures/hello3.png}
\end{center}
\begin{code}
<{:input:../code/hello3.hny}>
\end{code}
\caption{\harmonylink{code/hello3.hny} Harmony program with two possible outputs}
\label{fig:choice}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=0.15\textwidth]{figures/hello4.png}
\end{center}
\begin{code}
<{:input:../code/hello4.hny}>
\end{code}
\caption{\harmonylink{code/hello4.hny} Harmony program with an infinite number of outputs}
\label{fig:hello4}
\end{figure}

\begin{figure}[h]
\begin{center}
\begin{tabular}{ccc}
\includegraphics[width=0.45\textwidth]{figures/hello5.png}
& \rule{0.05\linewidth}{0in} &
\includegraphics[width=0.45\textwidth]{figures/hello6.png} \\
\begin{tcolorbox}[width=0.4\linewidth]
<{:input:../code/hello5.hny}>
\end{tcolorbox}
& \rule{0.05\linewidth}{0in} &
\begin{tcolorbox}[width=0.4\linewidth]
<{:input:../code/hello6.hny}>
\end{tcolorbox}
\\
(a) \harmonylink{code/hello5.hny} && (b) \harmonylink{code/hello6.hny}
\end{tabular}
\end{center}
\caption{Demonstrating Harmony methods and threads}
\label{fig:threads}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.9\textwidth]{figures/hello7.png}
\end{center}
\begin{code}
<{:input:../code/hello7.hny}>
\end{code}
\caption{\harmonylink{code/hello7.hny} Various interleavings of threads}
\label{fig:hello7}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=0.9\textwidth]{figures/hello8.png}
\end{center}
\begin{code}
<{:input:../code/hello8.hny}>
\end{code}
\caption{\harmonylink{code/hello8.hny} Making groups of operations atomic reduces interleaving}
\label{fig:hello8}
\end{figure}

@@

\begin{figure}[h]
\begin{code}
<{:input:../code/Up.hny}>
\end{code}
\caption{\harmonylink{code/Up.hny} Incrementing the same variable twice in parallel}
\label{fig:inc}
\end{figure}

@@

\begin{figure}
\begin{code}
\VerbatimInput[xleftmargin=5mm,numbers=left]{../python/UpMany.py}
\end{code}
\caption{\harmonylink{python/UpMany.py} Using Python to increment <{N}> times}
\label{fig:incmany}
\end{figure}

@@

\begin{figure}
\begin{code}
<{:input:../code/UpEnter.hny}>
\end{code}
\caption{\harmonylink{code/UpEnter.hny} Incorrect attempt at fixing the code of \autoref{fig:inc}}
\label{fig:incenter}
\end{figure}

@@

\begin{figure}
\begin{code}
<{:input:../code/UpLock.hny}>
\end{code}
\caption{\harmonylink{code/UpLock.hny} \autoref{fig:inc} fixed with a lock}
\label{fig:incfixed}
\end{figure}

@@

\begin{figure}
\begin{code}
<{:input:../code/locksusp.hny}>
\end{code}
\caption{\harmonylink{modules/synchS.hny} Lock implementation using suspension}
\label{fig:suspension}
\end{figure}

@@

\begin{figure}
\begin{code}
<{:input:../code/xy.hny}>
\end{code}
\caption{\harmonylink{code/xy.hny} Incomplete code for \autoref{ex:xy} with desired invariant $x + y = 100$}
\label{fig:xy}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.9\textwidth]{figures/consensus.png}
\end{center}
\begin{code}
<{:input:../code/consensus.hny}>
\end{code}
\caption{\harmonylink{code/consensus.hny} Distributed consensus code and behavior DFA}
\label{fig:consensus}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.95\textwidth]{figures/bosco.png}
\end{center}
\caption{The behavior DFA for \autoref{fig:bosco}}
\label{fig:boscodfa}
\end{figure}
